The finite base property for some subreducts of representable relation algebras

### 2020-07-12 problem-19.17/Text.tex
R(;, |): update the definition of a rainbow algebra according to Andreka/Maddux

\nocite{*}

@@

  \begin{enumerate}
    \item A relation algebra is an algebra $\mathcal{R} = \langle R, 0, 1, \wedge, \vee, \neg, ;, {}^{\smile}, {\bf 1 }\rangle$ such that $\langle R, 0, 1, \wedge, \vee, \neg \rangle$ is a Boolean algebra and the following
    equations hold, for each $a, b, c \in R$:
    \begin{enumerate}
      \item $a ; (b ; c) = (a ; b) ; c$
      \item $(a \vee b) ; c = (a ; c) \vee (b ; c)$
      \item $a ; {\bf 1} = a$
      \item $a^{\smile \smile} = a$
      \item $(a \vee b)^{\smile} = a^{\smile} \vee b^{\smile}$
      \item $(a ; b)^{\smile} = b^{\smile} ; a^{\smile}$
      \item $a^{\smile} ; (\neg (a ; b)) \leq \neg b$
    \end{enumerate}
    where $a \leq b$ iff $a \wedge b = a$ iff $a \vee b = b$. ${\bf RA}$ denotes the class of all relation
    algebras.
    \item A proper relation algebra is an algebra $\mathcal{R} = \langle R, 0, 1, \wedge, \vee, \neg, ;, {}^{\smile}, {\bf 1 }\rangle$ such that $R \subseteq \mathcal{P}(W)$, where $W$ is an equivalence relation; $0 = \emptyset$; $1 = W$; $\wedge$, $\vee$, $\neg$ are set-theoretic intersection, union, and
    complement respectively; $;$ is relation composition, ${}^{\smile}$ is relation converse, ${\bf 1}$ is a
    diagonal relation restricted to $W$, that is:
    \begin{enumerate}
    \item $a ; b = \{ \langle x, z \rangle \: | \: \exists y \: \langle x, y \rangle \in a \: \& \: \langle y, z \rangle \in b \}$
    \item $a^{\smile} = \{ \langle x, y \rangle \: | \: \langle y, x \rangle \in a \}$
    \item ${\bf 1} = \{ \langle x, y \rangle \: | \: x = y \}$
    \end{enumerate}
      The class of all proper relation algebras is denoted as ${\bf PRA}$. ${\bf Rs}$ is the class of all relation set algebras, proper relation algebra with a diagonal subrelation as an identity. ${\bf RRA}$ is the class of all representable relation algebras, that is, the closure of ${\bf PRA}$ under isomorphic copies. That is,
      ${\bf RRA} = {\bf IPRA}$.
  \end{enumerate}
\end{defin}
Note that the (quasi)equational theories of those classes coincide, that is
\begin{center}
  ${\bf IPRA} = {\bf RRA} = {\bf SP}{\bf Rs}$
\end{center}
Moreover, ${\bf RRA}$ is a variety, but it cannot be defined by any set of first-order formulas \cite{monk1964representable}.

@@

\begin{enumerate}
  \item $a \setminus b = \neg (a^{\smile} ; \neg b)$
  \item $a / b = \neg (\neg a ; b^{\smile})$
\end{enumerate}

@@

Given a subset of definable operations in ${\bf RA}$ $\tau$, we denote the class of subalgebras of the
$\tau$-reducts by ${\bf R}(\tau)$. The algebras containing to this class are defined as restrictions of
elements belonging to ${\bf Rs}$ to operations of $\tau$. By ${\bf Q}(\tau)$ we mean a quasivariety generated by $R(\tau)$. As in \cite{hirsch2011positive}, we put ${\bf Q}(\tau)$ as the closure of ${\bf R}(\tau)$ under subalgebras and products assuming that ${\bf R}(\tau)$ is already closed under ultraproducts.

@@

 A \emph{relation structure} (${\bf RS}$) is an arbitrary algebra of the signature $\Omega = \langle \cdot, \setminus, /, \leq \rangle$, where $\cdot, \setminus, /$ are binary function symbols and $\leq$ is a binary relation symbol.

\begin{defin}
  A residuated semigroup is an algebra $\mathcal{S} = \langle S, \cdot, \leq, \setminus, / \rangle$ such that $\langle S, \cdot, \leq, \rangle$ is an ordered residuated semigroup and the following equivalences hold for each $a, b, c \in S$:

  \begin{center}
    $b \leq a \setminus c \Leftrightarrow a \cdot b \leq c \Leftrightarrow a \leq c / b$
  \end{center}
  ${\bf ORS}$ is the class of all residuated semigroups.
\end{defin}

@@

\begin{defin}
  Let $\mathcal{A} = \langle A, \leq, \cdot, \setminus, / \rangle$ be a residuated semigroup. A representation of $\mathcal{A}$ is an inclusion map $h : \mathcal{A} \to \mathcal{A}'$,
  where $\mathcal{A}' \in {\bf RRS}$ such that:
  \begin{enumerate}
    \item $dom(\mathcal{A}') = \{ \hat{a} \: | \: a \in A\}$, where $\hat{a} = \{ (b, c) \: | \: b \leq a \cdot c \}$.
  \end{enumerate}
\end{defin}

@@

\begin{defin} A join-semilattice ordered semigroup (${\bf OS^{\vee}}$) is an algebra $\mathcal{S} = \langle S, \cdot, \vee \rangle$ such that $\langle S, \cdot \rangle$ is a semigroup, $\langle S, \vee \rangle$ is a join-semilattice and the following equations hold for each $a, b. c \in S$:

  \begin{enumerate}
    \item $a \cdot (b \vee c) = (a \cdot b) \vee (a \cdot c)$
    \item $(a \vee b) \cdot c = (a \cdot c) \vee (b \cdot c)$
  \end{enumerate}
\end{defin}
This class is clearly a variety since ${\bf OS^{\vee}}$ has the equational definition so far as $\vee$ is defined as an associative, idempotent, and commutative operation.

Let $A$ be a set of binary relations on some base set $W$ such that $R = \cup A$ is transitive and $\{ x, y \: | \: x R y \} = W$ as in Definition~\ref{rrs}. A representable join semilattice-ordered semigroup is an algebra isomorphic to some join semilattice-ordered semigroup having the form $\mathcal{A} = \langle A, |, \cup \rangle$ such that $;$ is a relation composition as above and $\cup$ is the set-theoretic union. If $\mathcal{A}$ is representable, then $R(;, \vee)$ Let us recall some of underlying facts about representable join semilattice-ordered semigroups \cite{andreka1991representations}:

@@

  \begin{enumerate}
    \item Let $\mathcal{A} = \langle A, \vee, \cdot \rangle$ be a join semilattice-ordered semigroup such that, for all $a, b \in A$:
    \begin{enumerate}
      \item If $a \nleq b$, then there exists an atom $c \leq a$ and $c \nleq b$.
      \item If $c \leq a \cdot b$ and $c$ is an atom, then there exists an atom $a' \leq a$ such that $c \leq a' \cdot b$.
    \end{enumerate}
    then $\mathcal{A}$ is representable.
    \item Let $\mathcal{A} = \langle A, \cdot \rangle$ be a posemigroup, then $\mathcal{A}$ is representable and such a representation preserve any existing finite suprema and infima, if
    \begin{enumerate}
      \item The set of atoms is closed under $\cdot$.
      \item $\mathcal{A}$ has enough atoms, that is, if $x \in \operatorname{At}(A)$ and $z, w \in A$, then $x \leq z \cdot w$ implies there exist atoms $z_1 \leq z$ and $w_1 \leq w$ such that $x \leq z_1 \cdot w_1$. If $z \nleq w$, then there exists an atom $x$ such that $x \leq z$ and $x \nleq w$.
    \end{enumerate}
  \end{enumerate}
\end{prop}

@@

\begin{theorem}
  The equational and quasiequational theories of $R(;,\vee)$ is not finitely based.
\end{theorem}

Let us provide a proof of this fact using the rainbow technique \cite{hirsch2002relation} to show that the complement of ${\bf ROS^{\vee}}$ is not closed ultraproducts. This construction sometimes exploits the similar construction used by Andr{\'e}ka \cite{andreka1991representations} and by Maddux \cite{maddux_1989}.
We note that representability is not decidable for finite relation algebras \cite{hirsch2001representability} and this result has several generalisations \cite{hirsch2012undecidability}. Moreover, representability is undecidable for lattice-ordered semigroups and ordered complemented semigroups \cite{neuzerling2016undecidability}. We use(more or less) a standard way of showing that the class of certain reducts of representable relation algebras has no finite axiomatisation, see \cite{hodkinson2000axiomatizability} \cite{hirsch1997step}.

First of all, we recall several definitions such as colourings. We define a sequence of relation algebras $\{ \mathfrak{A}_n \}_{n < \omega}$ each of which belongs to ${\bf RA}$. We need these algebras to show that their $\{;, \vee\}$-reducts are not representable. That is, we are seeking to show that

Given $n < \omega$, the set of atoms $\operatorname{At}(\mathfrak{A}_n)$ consists of the following elements:
\begin{itemize}
\item identity: ${\bf 1}$, an atom with no colour
\item greens: ${\bf g}_i$ for $0 \leq i \leq 2^n$
\item yellow: ${\bf y}$
\item black: ${\bf b}$
\item whites: ${\bf w}$, ${\bf w}_{ij}$ for $0 \leq i \leq j \leq 2^n$
\item reds: ${\bf r}_i$ for $0 < i \leq 2^n$
\end{itemize}
We claim that every atom is self-converse ($a^{\smile} = a$). Given $x, y, z \in \mathfrak{A}_n$, a triple $(x,y,z)$ is an  inconsistent triangle if
\begin{center}
$x \land (y ; z) = y \land (z ; x) = z \land (x ; y) = 0$
\end{center}
We define the set of inconsistent triangles explicitly as follows.
\begin{itemize}
  \item $(x, y, {\bf 1})$ unless $x = y$
  \item $({\bf g}_i, {\bf g}_k, {\bf g}_l)$ for $i, k, l \leq 2^n$
  \item $({\bf y}, {\bf y}, {\bf y})$
  \item $({\bf y}, {\bf y}, {\bf b})$
  \item $({\bf g}_i, {\bf g}_j, {\bf w}_{kl})$ for $i, j \leq 2^n$ and $k, j \leq 2^n$
  \item $({\bf r}_i, {\bf r}_j, {\bf r}_k)$ unless $i + k = j$ or $i + k = j$ or $j + k = i$
  \item $({\bf g}_i, {\bf g}_{i + 1}, {\bf r})$ unless $j = 1$
  \item $({\bf g}_i, {\bf y}, {\bf w}_{jk})$ unless $i \in \{ j, k \}$
\end{itemize}
$({\bf g}_i, {\bf g}_i, {\bf w}_{kj})$ stands for ${\bf g}_i \land ({\bf g}_i ; {\bf w}_{kj}) = {\bf g}_i \land ({\bf w}_{kj} ; {\bf g}_i) = {\bf w}_{kj} \land ({\bf g}_i ; {\bf g}_i) = 0$, and so on.

$C$ is the set of consistent triangles defined as

\begin{center}
  $C = \{ (a, b, c ) \: | \: a,b,c \in \operatorname{At}(\mathfrak{A}_n), (a,b,c) \text{ is consistent}\}$
\end{center}

Let us ensure briefly that $\mathfrak{A}_n$ is indeed a relation algebra defining the multiplication table for composition as in \cite{lyndon1950representation}. For that, it is enough to show associativity for atoms $a, x, y, z$ such that $a \leq (x ; y) ; z$. For that, one needs to find an atom $b$ such that $a \leq x ; b$ and $b \leq y ; z$. If $x = y$, then we put $b = {\bf 1}$. Otherwise, we try to use a white atom or a black atom for $b$ unless $x, a$ are green and $y, z$ are yellow.
Suppose $x = {\bf g}_i$, $a = {\bf g}_j$, $y = {\bf y}_k$, and $z = {\bf y}_l$, then we put

\begin{lemma}
  For each $n < \omega$, $\mathfrak{A}_n$ does not belong ${\bf RRA}$. The $(\vee, ;)$-reduct $\mathfrak{S}_n$ of $\mathfrak{A}_n$ is not representable as well. For each $n < \omega$, there is an equation valid in set algebras failing in $\mathfrak{S}_n$.
\end{lemma}

\begin{proof}
  See \cite{hodkinson2000axiomatizability} to have a proof that $\mathfrak{A}_n \notin {\bf RRA}$. However, we leave a proof sketch.

  We prove that $\mathfrak{S}_n$ is not representable by contradiction.
  Suppose $h$ is an isomorphism of $\mathfrak{S}_n$ to a set relation of relations having similarity type $\{ ;, \vee \}$. Let $0$ be a zero element of $\mathfrak{A}_n$.
\end{proof}

Let us define networks and games according to \cite{hirsch1997step}.

@@

\begin{lemma}
  Any non-trivial ultraproduct of $\{ \mathfrak{A}_n \}_{n < \omega}$ is representable, that is, belongs to ${\bf RRA}$. The same statement for non-trivial ultraproduct of reducts $\{ \mathfrak{S}_n \}_{n < \omega}$ that belongs to $R(;, \vee)$.
\end{lemma}

@@

\subsection{The finite algebra on finite base for $R(;, \vee)$ (or its failure)}

>>>>

@@

    A relation algebra is an algebra $\mathcal{R} = \langle R, 0, 1, +, -, ;, {}^{\smile}, {\bf 1 }\rangle$ such that $\langle R, 0, 1, +, - \rangle$ is a Boolean algebra and the following
    equations hold, for each $a, b, c \in R$:
    \begin{enumerate}
      \item $a ; (b ; c) = (a ; b) ; c$
      \item $(a + b) ; c = (a ; c) + (b ; c)$
      \item $a ; {\bf 1} = a$
      \item $a^{\smile \smile} = a$
      \item $(a + b)^{\smile} = a^{\smile} + b^{\smile}$
      \item $(a ; b)^{\smile} = b^{\smile} ; a^{\smile}$
      \item $a^{\smile} ; (- (a ; b)) \leq - b$
    \end{enumerate}
    where $a \leq b$ iff $a + b = b$. ${\bf RA}$ denotes the class of all relation
    algebras.
\end{defin}
A relation algebra is called symmetric, if every element is self-converse. A relation algebra is called integral, if
\begin{center}
  $a ; b = 0 \Rightarrow a = 0 \text{ or } b = 0$.
\end{center}

\begin{defin}
    A proper relation algebra is an algebra $\mathcal{R} = \langle R, 0, 1, \cup, -, |, {}^{\smile}, {\bf 1 }\rangle$ such that $R \subseteq \mathcal{P}(W)$, where $W$ is an equivalence relation; $0 = \emptyset$; $1 = W$; $\cap$, $\cup$, $-$ are set-theoretic intersection, union, and
    complement respectively; $|$ is relation composition, ${}^{\smile}$ is relation converse, ${\bf 1}$ is a
    diagonal relation restricted to $W$, that is:
    \begin{enumerate}
    \item $a | b = \{ \langle x, z \rangle \: | \: \exists y \: \langle x, y \rangle \in a \: \& \: \langle y, z \rangle \in b \}$
    \item $a^{\smile} = \{ \langle x, y \rangle \: | \: \langle y, x \rangle \in a \}$
    \item ${\bf 1} = \{ \langle x, y \rangle \: | \: x = y \}$
    \end{enumerate}
      The class of all proper relation algebras is denoted as ${\bf PRA}$. ${\bf Rs}$ is the class of all relation set algebras, proper relation algebra with a diagonal subrelation as an identity. ${\bf RRA}$ is the class of all representable relation algebras, that is, the closure of ${\bf PRA}$ under isomorphic copies. That is,
      ${\bf RRA} = {\bf IPRA}$.
\end{defin}
Note that the (quasi)equational theories of those classes coincide, that is
\begin{center}
  ${\bf IPRA} = {\bf RRA} = {\bf SP}{\bf Rs}$
\end{center}
Moreover, ${\bf RRA}$ is a variety, but it cannot be defined by any set of first-order formulas \cite{monk1964representable}.

@@

\begin{enumerate}
  \item $a \setminus b = -(a^{\smile} ; -b)$
  \item $a / b = - (- a ; b^{\smile})$
\end{enumerate}

@@

Given a subset of definable operations in ${\bf RA}$ $\tau$, we denote the class of subalgebras of the
$\tau$-reducts by ${\bf R}(\tau)$. The algebras containing to this class are defined as restrictions of
elements belonging to ${\bf Rs}$ to operations of $\tau$. By ${\bf Q}(\tau)$ we mean a quasivariety generated by ${\bf R}(\tau)$. As in \cite{hirsch2011positive}, we put ${\bf Q}(\tau)$ as the closure of ${\bf R}(\tau)$ under subalgebras and products assuming that ${\bf R}(\tau)$ is already closed under ultraproducts.

@@

 A \emph{relation structure} (${\bf RS}$) is an arbitrary algebra of the signature $\Omega = \langle \circ, \setminus, /, \leq \rangle$, where $\circ, \setminus, /$ are binary function symbols and $\leq$ is a binary relation symbol.

\begin{defin}
  A residuated semigroup is an algebra $\mathcal{S} = \langle S, \circ, \leq, \setminus, / \rangle$ such that $\langle S, \circ, \leq, \rangle$ is an ordered residuated semigroup and the following equivalences hold for each $a, b, c \in S$:

  \begin{center}
    $b \leq a \setminus c \Leftrightarrow a \circ b \leq c \Leftrightarrow a \leq c / b$
  \end{center}
  ${\bf ORS}$ is the class of all residuated semigroups.
\end{defin}

@@

\begin{defin}
  Let $\mathcal{A} = \langle A, \leq, ;, \setminus, / \rangle$ be a residuated semigroup. A representation of $\mathcal{A}$ is an inclusion map $h : \mathcal{A} \to \mathcal{A}'$,
  where $\mathcal{A}' \in {\bf RRS}$ such that:
  \begin{enumerate}
    \item $dom(\mathcal{A}') = \{ \hat{a} \: | \: a \in A\}$, where $\hat{a} = \{ (b, c) \: | \: b \leq a ; c \}$.
  \end{enumerate}
\end{defin}

@@

\begin{defin} A join-semilattice ordered semigroup (${\bf OS^{+}}$) is an algebra $\mathcal{S} = \langle S, ;, + \rangle$ such that $\langle S, ; \rangle$ is a semigroup, $\langle S, + \rangle$ is a join-semilattice and the following equations hold for each $a, b. c \in S$:

  \begin{enumerate}
    \item $a ; (b + c) = (a ; b) + (a ; c)$
    \item $(a + b) ; c = (a ; c) + (b ; c)$
  \end{enumerate}
\end{defin}
This class is clearly a variety since ${\bf OS^{+}}$ has the equational definition so far as $+$ is defined as an associative, idempotent, and commutative operation.

Let $A$ be a set of binary relations on some base set $W$ such that $R = \cup A$ is transitive and $\{ x, y \: | \: x R y \} = W$ as in Definition~\ref{rrs}. A representable join semilattice-ordered semigroup is an algebra isomorphic to some join semilattice-ordered semigroup having the form $\mathcal{A} = \langle A, |, \cup \rangle$ such that $;$ is a relation composition as above and $\cup$ is the set-theoretic union. If $\mathcal{A}$ is representable, then $\mathcal{A} \in {\bf I}({\bf R}(\cup, |))$. Let us recall some of underlying facts about representable join semilattice-ordered semigroups \cite{andreka1991representations}:

@@

  \begin{enumerate}
    \item Let $\mathcal{A} = \langle A, +, ; \rangle$ be a join semilattice-ordered semigroup such that, for all $a, b \in A$:
    \begin{enumerate}
      \item If $a \nleq b$, then there exists an atom $c \leq a$ and $c \nleq b$.
      \item If $c \leq a ; b$ and $c$ is an atom, then there exists an atom $a' \leq a$ such that $c \leq a' \cdot b$.
    \end{enumerate}
    then $\mathcal{A}$ is representable.
    \item Let $\mathcal{A} = \langle A, ; \rangle$ be a posemigroup, then $\mathcal{A}$ is representable and such a representation preserve any existing finite suprema and infima, if
    \begin{enumerate}
      \item The set of atoms is closed under $;$.
      \item $\mathcal{A}$ has enough atoms, that is, if $x \in \operatorname{At}(A)$ and $z, w \in A$, then $x \leq z ; w$ implies there exist atoms $z_1 \leq z$ and $w_1 \leq w$ such that $x \leq z_1 ; w_1$. If $z \nleq w$, then there exists an atom $x$ such that $x \leq z$ and $x \nleq w$.
    \end{enumerate}
  \end{enumerate}
\end{prop}

@@

\begin{theorem}
  ${\bf R}(\cup, |)$ is not finitely axiomatisable.
\end{theorem}

Let us provide a proof of this fact using the rainbow technique \cite{hirsch2002relation} to show that the complement of ${\bf ROS^{+}}$ is not closed ultraproducts. This construction sometimes exploits the similar construction used by Andr{\'e}ka \cite{andreka1991representations} and by Maddux \cite{maddux_1989}.
We note that representability is not decidable for finite relation algebras \cite{hirsch2001representability} and this result has several generalisations \cite{hirsch2012undecidability}. Moreover, representability is undecidable for lattice-ordered semigroups and ordered complemented semigroups \cite{neuzerling2016undecidability}. We use (more or less) a standard way of showing that the class of certain reducts of representable relation algebras has no finite axiomatisation, see \cite{hodkinson2000axiomatizability} \cite{hirsch1997step}.

First of all, we recall several definitions such as colourings. We provide a sequence of symmetric, integral, finite relation algebras $\{ \mathfrak{A}_n \}_{n < \omega}$ such that $\mathfrak{A}_n \notin {\bf RRA}$. The statement has been proved by Andreka \cite{andreka1991representations} and reproduced here \cite{andreka2011axiomatizability}.

Given $n < \omega$, the set of atoms $\operatorname{At}(\mathfrak{A}_n)$ consists of the following elements:
\begin{itemize}
\item identity: ${\bf 1}$, an atom with no colour,
\item white: ${\bf w}$,
\item greens: ${\bf g}_i$ for $1 \leq i \leq n$,
\item yellows: ${\bf y}_i$ for $1 \leq i \leq n$,
\item ivory: ${\bf i}$,
\item reds: ${\bf r}_i$ for $1 \leq i \leq n$,
\item blacks: ${\bf b}_i$ for $1 \leq i \leq n$.
\end{itemize}

We have the following steps:

\vspace{\baselineskip}

{\bf Step 1}. Let $\mathcal{A}_n$ be the upper semilattice presented with the set $\operatorname{At}(\mathfrak{A}_n) \cup \{ 0 \}$ and the following relations for each $x \in \operatorname{At}(\mathfrak{A}_n)$ and for each $1 \leq i \leq n$.
\begin{enumerate}
  \item ${\bf w} \leq {\bf g}_i + {\bf y}_i$,
  \item ${\bf i} \leq {\bf y}_i + {\bf r}_i$,
  \item $x + 0 = x$
\end{enumerate}

{\bf Step 2}. We define $S$, the set of two element subsets of $\mathcal{A}_n$:
\begin{center}
  $S = \{ \{ {\bf w}, {\bf r}_1 \} \} \cup \{ \{ {\bf g}_i, {\bf b}_i \} \: | \: 1 \leq i \leq n \} \cup
  \{ \{ {\bf y}_i, {\bf r}_i \} \: | \: 1 \leq i < n \} \cup \{ \{ {\bf y}_n, {\bf i}\} \}$.
\end{center}

{\bf Step 3}. The operations on $\mathfrak{A}_n$:
\begin{enumerate}
  \item $1 = \sum \operatorname{At}(\mathcal{A}_n) \cup \{ 0 \}$,
  \item $0 = \O$,
  \item $x = x^{\smile}$,
  \item $0 ; x = 0 ; x = 0$,
  \item ${\bf 1} ; x = {\bf 1} ; x = x$,
  \item $x ; y = \begin{cases} {\bf i}, \text{ if $\{x, y\} \in S$} \\ 1, \text{ otherwise } \end{cases}$ \\ unless $x, y \in \{ 0, {\bf 1}\}$.
\end{enumerate}

{\bf Step 4}. Define the following quasi-idenity:
\begin{center}
  $\begin{array}{lll}
  & q_n = \bigwedge \limits_{1 \leq i \leq n} ( (x \leq x^{'}_i + x^{''}_i) \land (y \leq y^{'}_i + y^{''}_i)) \to & \\
  & x ; y \leq x ; y^{'}_1 + \sum \limits_{1 \leq i < n} (x^{'}_i ; y^{''}_i + x^{''}_i ; y^{'}_{i + 1}) + x^{'}_n ; y^{''}_n + x^{''}_n ; y&
  \end{array}$
\end{center}

\begin{lemma}

  \begin{enumerate}
    \item $q_n$ is valid in ${\bf RRA}$ for each $n < \omega$.
    \item $q_n$ fails in $\mathfrak{A}_n$.
  \end{enumerate}
\end{lemma}

\begin{proof}
  The valuation $\vartheta$ defined as:
  \begin{enumerate}
    \item $\vartheta(x) = {\bf w}$
    \item $\vartheta(x_i^{'}) = {\bf g}_i$
    \item $\vartheta(x_i^{''}) = {\bf y}_i$
    \item $\vartheta(y) = {\bf i}$
    \item $\vartheta(y_i^{'}) = {\bf r}_i$
    \item $\vartheta(y_i^{''}) = {\bf b}_i$
  \end{enumerate}
  falsifies $q_n$ in $\mathfrak{A}_n$
\end{proof}

The second is to show that any non-trivial ultraproduct $\prod \limits_{D} \mathfrak{A}_n \in {\bf RRA}$, where $D$ is an ultrafilter over $\mathcal{P}(\omega)$. We show that via the rainbow technique. Let us define networks and games according to \cite{hirsch1997step}.

@@

\begin{lemma}
  Any non-trivial ultraproduct of $\{ \mathfrak{A}_n \}_{n < \omega}$ is representable, that is, belongs to ${\bf RRA}$. The same statement for non-trivial ultraproduct of reducts $\{ \mathfrak{S}_n \}_{n < \omega}$ that belongs to ${\bf R}(\cup, |)$.
\end{lemma}

@@

\subsection{The finite algebra on finite base for ${\bf R}(\cup, |)$ (or its failure)}
